### 2020-07-13 response/response-demography-3.tex

In the Data section, I have also changed the discussion of the imposed censoring 
clearer by specifying the cut-offs for both the spell duration and the birth interval.
In the ``How Birth Spacing Changed'' section, I explain that I add nine month
to the estimated spell length to get to birth intervals.
In the ``Mortality and the Changing Birth Spacing'' section, I retained the
definition of the periods but updated the numbers and the discussion of
results so they reflect birth intervals rather than pregnancy intervals.

\item Please include a brief discussion or footnote about the quality of
birth date data in the DHS/NSFH and how this could bias your results or
not.

[Response:]

I have expanded the discussion of the birth history data in the ``Data'' section and
why it is important.
As part of this expanded discussion, I included more information about systematic
recall error, why it is likely the main concern here, what the effect is on the
estimates, and how I address this problem.
I have also included a reference to \citet{Schoumaker2014} that finds that the first
rounds of the NFHS are of ``moderate quality,'' although that is without the correction
for recall error that I use.

@@

\item Perhaps the conclusion could start with a brief overview of your
topic and research question again to remind the reader of the overall
motivation for the study.

[Response:]

I have added a brief synopsis of the changes in India in the beginning of
the Conclusion and recap the three questions after that.
I have also slightly edited the Conclusion to tie better with the 
questions.

### 2020-07-13 paper/sex_selection_spacing-ver4.tex
Add Schoumaker 2014 footnote and remove footnote on probing procedure in NFHS

In addition to a large number of women surveyed and the long period covered, a significant 
benefit of the NFHS over other surveys is that enumerators pay careful attention to the 
spacing between births and probe for ``missed'' births.%
\footnote{
The method used to probe for missing births depends on the survey.
NFHS-1 probe for each calendar birth interval that is four or more years.
NFHS-2 asked for stillbirths, spontaneous and induced abortions, and also probed 
for each calendar birth interval four or more years.
NFHS-3 and NFHS-4 did not directly use birth intervals, but asked whether there were any 
other live births between (name of previous birth) and (name), including any children who 
died after birth, and asked for births before the birth listed as first birth and
after the last birth listed as the last birth.
}
The quality of the birth date data is especially important here since the reliability of the 
results depends on the correctness of the birth histories provided by the respondents.
The main concern is underreporting of deceased children, especially a systematic recall error 
where respondents' likelihood of reporting the birth of a deceased child depends 
on the sex of that child.
To establish the quality of the birth interval data, I provide a detailed discussion of the 
degree of systematic recall error in the Online Appendix.
Recall error appear heavily dependent on how long ago a woman was married, 
and I, consequently, drop women married 22 years or more.

>>>>

In addition to a large number of women surveyed and the long period covered, a significant 
benefit of the NFHS over other surveys is that enumerators pay careful attention to the 
spacing between births and probe for ``missed'' births.
The quality of the birth date data is crucial since the reliability of the results depends 
on the correctness of the birth histories provided by the respondents.
For India, the main concern is underreporting of deceased children, especially a systematic 
recall error where respondents' likelihood of reporting the birth of a deceased child depends 
on the sex of that child.
If deceased children are not reported the birth intervals will be inflated and likely make 
the changes over time appear smaller than they really are.
I, therefore, provide a detailed analysis of systematic recall error in the Online Appendix.
Recall error is heavily dependent on how long ago a woman was married, and I, consequently, 
drop women married 22 years or more.%
\footnote{
\citet{Schoumaker2014} discusses the quality of birth histories in DHS surveys and the 
impact on fertility estimates.
Although that analysis does not directly examine systematic recall error, it is likely that
it explain why the first rounds of NFHS are listed as ``moderate quality.''
}
